---
title: "Plotly and flexdashboard"
output: html_document
---
For this example, I`ll create a new .Rmd file that knits to .html in the repo / R Project holding the website I made in making websites. In addition to some usual packages, I`ll load plotly.
```{r, setup}
library(tidyverse)
library(p8105.datasets)

library(plotly)
```


We`re going to focus on the Airbnb data for this topic. The code below extracts what we need right now; specifically, we select only a few of the variables, filter to include a subset of the data, and down-sample for computational efficiency.

```{r}
data(nyc_airbnb)

nyc_airbnb = #big data set, need to zoom in and zoom out
  nyc_airbnb %>% 
  mutate(rating = review_scores_location / 2) %>%#10 star to five star
  select(
    neighbourhood_group, neighbourhood, rating, price, room_type, lat, long) %>%
  filter(
    !is.na(rating), 
    neighbourhood_group == "Manhattan",
    room_type == "Entire home/apt",
    price %in% 100:500) %>% 
  drop_na(rating)
```

## make a scatterplot
We`ll use this dataset as the basis for our plots.

Plotly scatterplot
There are several practical differences comparing ggplot and plot_ly, but the underlying conceptual framework is similar. We need to define a dataset, specify how variables map to plot elements, and pick a plot type.

Below we`re plotting the location (latitude and longitude) of the rentals in our dataset, and mapping price to color. We also define a new variable text_label and map that to text.

The type of plot is scatter, which has several `modes`: markers produces the same kind of plot as ggplot::geom_point, lines produces the same kind of plot as ggplot::geom_line.


```{r}
nyc_airbnb %>%
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating)) %>% #creat a string variable. "\nRating: "get a new line, names Rating.
  plot_ly(
    x = ~lat, y = ~long, type = "scatter", mode = "markers",
    color = ~price, text = ~text_label, alpha = 0.5)#use zoom to zoom in and out(double click to get back____get a squar  to zoom in )
```

##Plotly boxplot
Next up is the boxplot. The process for creating the boxplot is similar to above: define the dataset, specify the mappings, pick a plot type. Here the type is box, and there aren¡¯t modes to choose from.

```{r}
nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "viridis")#click the name to hide it, and double click a name to only see it.
```

```{r}
nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(y = ~price, color = ~neighbourhood, type = "bar", colors = "viridis")
```

##ggplotly

```{r}
gg_lat_long = 
nyc_airbnb %>% 
  ggplot(aes(x = lat, y= long, color = price)) +
  geom_point()

ggplotly(gg_lat_long)
```

#dashboard r markdown(start a nes .rmd)
source_code:(embed)

```{r}
library(flexdashboard)
```

column{dara-width = 350}

#chart A
```{r}
nyc_airbnb %>%
  mutate(text_label = str_c("Price: $", price, "\nRating: ", rating)) %>% #creat a string variable. "\nRating: "get a new line, names Rating.
  plot_ly(
    x = ~lat, y = ~long, type = "scatter", mode = "markers",
    color = ~price, text = ~text_label, alpha = 0.5)

```

#chart B
```{r}
nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(y = ~price, color = ~neighbourhood, type = "box", colors = "viridis")
```

put
rmarkdown::render("dashboard_template.Rmd", output_format = "flexdashboard::flex_dashboard")
in the console and run, it will make the dashboard always run out as a dash board insteading of the normal html.